# Methods

This section describes the closed-loop simulation framework
developed for testing a proposed WCVI herring re-opening
procedure. We first describe the three operating models used
to represent alternative hypotheses about WCVI herring
population dynamics. We then describe the management
procedure, including the assessment model, the harvest control
rule, and the spatial TAC allocation methods. Finally, we
describe the simulation design and performance metrics.

## Operating models

Three operating models (OMs) are used to represent the range
of assumptions about WCVI herring population dynamics. All
three OMs are conditioned on historical data from 1951 to
2024 and share the same data inputs (catch, spawn indices, and
age composition). They differ in their treatment of natural
mortality and spatial structure.

### *SISCAH-DDM*: density-dependent mortality

The *SISCAH-DDM* model is the current basis for DFO Pacific
Herring stock assessments [@johnson2024SCAH]. It treats WCVI
herring as a single panmictic stock with density-dependent
natural mortality, where natural mortality rates increase at
low stock sizes. Under this model, unfished biomass is
approximately 42 kt, $B_{MSY}$ is approximately 17.35 kt,
the limit reference point (LRP) is $0.3 B_0 \approx 13.5$ kt,
and the maximum sustainable yield is approximately 1.6 kt.

```{r fig-yieldCurve, fig.cap = capYieldCurve}
capYieldCurve <- paste0(
  "Simulation-based equilibrium yield curve for the \\emph{SISCAH-DDM} ",
  "operating model, showing spawning biomass (kt) on the x-axis and ",
  "equilibrium yield (kt) on the y-axis. Vertical dashed lines indicate ",
  "key reference points: LRP ($0.3B_0$), $0.4B_{MSY}$, $0.8B_{MSY}$, ",
  "$B_{MSY}$, $B_0$, and $B_{ref}$ (17.35 kt, from the 2023 CSAS review).")
plotYieldCurve(
  empRC   = saveEmpRefCurves,
  histRpt = DDMfit,
  Bref    = 17.35)
```

### *SISCAH-1S-Pred*: single-stock with predation

The *SISCAH-1S-Pred* model treats WCVI herring as a single
stock but replaces density-dependent mortality with explicit
predation mortality from four major predator groups: Humpback
Whales, Steller Sea Lions, Harbour Seals, and Pacific Hake
[@doherty2024predation]. Predation mortality is modelled
using functional response relationships and is driven by
estimated predator abundance trends. Under this model,
unfished biomass is approximately 26.2 kt, substantially
lower than the *SISCAH-DDM* estimate, reflecting higher total
natural mortality when predation is included explicitly.

### *SISCAH-3S-Pred*: three-stock with predation {#sec:3SpredM}

The *SISCAH-3S-Pred* model, developed in Phase 2 of this
project [@lfr2025_NTC], splits the WCVI herring population
into three independent stocks corresponding to Stat Areas 23, 24,
and 25. Each stock is fit independently to Stat Area-level catch,
spawn index, and age composition data. Predation mortality
is included as in *SISCAH-1S-Pred*, with coast-wide predator
consumption allocated among Stat Areas in proportion to vulnerable
biomass.

The aggregate unfished biomass under *SISCAH-3S-Pred* is
approximately 17.1 kt, which is close to the $B_{MSY}$
estimate from the *SISCAH-DDM* model. This means that the
minimum escapement reference point ($B_{ref} = B_{MSY|DDM}$)
used in the harvest control rule is near the operating model's
unfished biomass level, leading to frequent fishery closures.

Using *SISCAH-3S-Pred* as an operating model while the
management procedure assumes a single stock creates a
structural mismatch that tests the robustness of the MP to
unrecognised spatial structure and predation.

```{r fig-histSSB, fig.cap = capHistSSB, fig.asp = 0.65}
capHistSSB <- paste0(
  "Historical spawning biomass (kt) from all three operating ",
  "models (1951--2023). Solid lines show aggregate SSB for ",
  "\\emph{SISCAH-DDM} (black), \\emph{SISCAH-1S-Pred} (blue), ",
  "and \\emph{SISCAH-3S-Pred} (red). Dashed lines show ",
  "per-Stat Area SSB under \\emph{SISCAH-3S-Pred}. Horizontal ",
  "dotted lines indicate equilibrium unfished biomass ($B_0$) ",
  "for each OM, colour-coded to match.")
plotHistSSB(DDMfit = DDMfit, fit1S = fit1S, fit3S = fit3S)
```

## Management procedure

The management procedure consists of two steps: (i) an
aggregate stock assessment that determines a coastwide TAC,
and (ii) a spatial allocation step that distributes the TAC
among Stat Areas.

### Step 1: aggregate assessment and harvest control rule

In the first step, data from all three Stat Areas are
aggregated into a single coastwide data set. Spawn indices
are summed across Stat Areas, catches are summed, and
weight-at-age is averaged. A single-stock *SISCAH-DIM*
(density-independent mortality) assessment model is then
fit to the aggregated data to estimate current spawning
biomass. The *SISCAH-DIM* model is the adopted assessment
model for BC Herring stock assessment regions (SARs) that
currently have management procedures and prosecute TACs.

The harvest control rule (HCR) is a minimum escapement rule
similar to the current DFO rule for BC herring. The rule has
two parameters:

- $B_{ref}$: a preliminary minimum escapement biomass
  of approximately 17.35 kt, which is the $B_{MSY}$
  value estimated in the 2023 CSAS research document 
  where *SISCAH-DDM* was first published 
  [@johnson2024SCAH]; and
- $U_{ref}$: the maximum harvest rate of 8.47\%,
   resulting from some preliminary tuning under 
   the DDM OM.

The HCR operates as follows:

\begin{equation}
U_t = \begin{cases}
0 & \text{if } \hat{B}_t \leq B_{ref} \\
\displaystyle U_{ref} \cdot \left(1 -
  \frac{B_{ref}}{\hat{B}_t} \right) &
  \text{if } \hat{B}_t > B_{ref}
\end{cases}
\end{equation}

\noindent where $\hat{B}_t$ is the estimated aggregate
spawning biomass from the assessment model and $U_t$ is
the harvest rate applied in year $t$. The TAC is then
$\text{TAC}_t = U_t \cdot \hat{B}_t$. When biomass is at
or below $B_{ref}$, the fishery is closed. When biomass
exceeds $B_{ref}$, the TAC is the surplus above $B_{ref}$,
up to a maximum harvest rate of $U_{ref}$.

```{r fig-HCRdiagram, fig.cap = capHCRdiagram, fig.asp = 1.1}
capHCRdiagram <- paste0(
  "Minimum escapement harvest control rule. Upper panel: harvest rate ",
  "$U_t$ as a function of assessed spawning biomass $\\hat{B}_t$. ",
  "Lower panel: TAC as a function of $\\hat{B}_t$. The shaded region ",
  "indicates the closed fishery ($\\hat{B}_t \\leq B_{ref}$). ",
  "Parameters: $B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$.")
plotHCRDiagram(Bref = 17.35, Uref = 0.0847)
```

### Step 2: spatial TAC allocation {#sec:allocation}

In the second step, the aggregate TAC is distributed among
Stat Areas. Three allocation methods are tested:

1. **Spawn index (SI) allocation**: the TAC is allocated in
   proportion to the average spawn index observed in each
   Stat Area over the most recent three years. This method uses
   the most current data on relative abundance to guide
   allocation.

2. **Catch allocation**: the TAC is allocated in proportion
   to the average catch taken in each Stat Area over the most
   recent years with non-zero catches. This method reflects
   historical fishing patterns.

3. **All Stat Area 23 allocation**: the entire TAC is allocated to
   Stat Area 23 (Barkley Sound). This method represents a scenario
   where fishing is concentrated in a single area, which may
   reflect operational preferences or access considerations.

Within each Stat Area, the allocated TAC is further distributed
among commercial fleets (seine roe, gillnet, and spawn-on-kelp
or bough) according to fixed fleet allocation proportions.

## Simulation design

Closed-loop simulations project the operating model forward
from the end of the historical period (2023) for 10 years under 
the management procedure described above. Simulations
apply the following steps in each projection year

1. Simulate observational data from the true population state, 
   including a simulated blended spawn index with randomised
   dive/surface survey ratios and log-normal observation
   errors parameterised from historical residuals, as well
   as catch-at-age data. If in a spatial OM, aggregate 
   observation data across statistical areas.
2  Fit the single-stock SISCAH-DIM assessment model;
3. Apply the harvest control rule to SISCAH-DIM estimates to 
   derive aggregate TAC. If in a spatial OM, TAC is allocated 
   among Stat Areas using the chosen allocation method;
5. Remove catch from the simulated population (either WCVI scale
   or individual statistical areas);
6. Advance the OM population forward by one year, including
   recruitment, natural mortality, and predation.

Simulations are repeated across 100 stochastic replicates
to capture uncertainty in future recruitment, basal mortality, 
and predator abundance. Operating model parameters are fixed 
at their maximum likelihood estimates (MLEs).

## Performance metrics

We evaluate performance at the WCVI SAR scale using metrics
applied in other BC herring regions. Selected metrics include

1. **pLRP**: the probability of maintaining spawning
   biomass above the limit reference point ($0.3 B_0$).
   The conservation objective requires pLRP $\geq$ 75\%
   over three herring generations.

2. **MAC10**: median average commercial catch over the first
10 projection years.

3. **MAS10**: median average spawn-on-bough catch over the
first 10 projection years.

4. **Openings**: Median number of years with fishery openings.

5. **pViable**: The probability of catch being above 650 t.

At the Stat Area level, there are no formal biological reference points 
or objectives. Therefore, we define the following metrics for performance
at the individual Stat Area level:

1. **Probability of low biomass**: the proportion of
   projection years and replicates in which spawning biomass
   in a given Stat Area falls below its historical minimum
   observed biomass over the entire conditioning period
   (1951--2024).

2. **Probability of low catch**: the proportion of projection
   years and replicates in which the catch from a given
   Stat Area falls below its historical minimum non-zero
   catch over the entire conditioning period (1951--2024).

These metrics provide a relative measure of how each
allocation method affects the risk of poor outcomes at the
Stat Area level. Because formal Stat Area-level comparisons
are only relevant under the spatially structured
*SISCAH-3S-Pred* OM, these metrics are computed for the
three-stock OM only. Aggregate performance under the
single-stock OMs is evaluated qualitatively from simulation
projection figures.
