# Results

Results are presented for each operating model in turn,
starting with the *SISCAH-DDM* operating model where the RP
assumptions are well matched, followed by the
*SISCAH-1S-Pred* and *SISCAH-3S-Pred* robustness tests.

## Reference case: *SISCAH-DDM* operating model

### Biological reference points

Under the *SISCAH-DDM* operating model, the yield curve
produces an unfished biomass of approximately 42 kt,
$B_{MSY} \approx 17.35$ kt, a limit reference point of
$0.3 B_0 \approx 13.5$ kt, and a maximum sustainable yield
of approximately 1.6 kt. The LRP and $B_{MSY}$ are close
together, meaning that the stock transitions relatively
quickly from a productive state to one requiring closure.

### RP performance

When the RP is applied to the *SISCAH-DDM* operating model,
performance is consistent with expectations given that the
assessment model and OM share the same structural assumptions.
The assessment model (*SISCAH-DIM*) estimates biomass
reasonably well, with no major evidence of bias during the
projection period. Median projected biomass remains well above
$B_{ref} \approx B_{MSY|DDM}$, and biomass is maintained
above the LRP ($0.3 B_0$) 96\% of the time (pLRP),
exceeding the 75\% conservation objective. Median
average commercial catch over 10 years (MAC10) is
approximately 1,900 t, and median average SOB yield
(MAS10) is approximately 15 t. The fishery is open in
all 10 projection years. The effective harvest rates
applied during the projection period are consistent
with the intended HCR
(Figures \@ref(fig:fig-DDMprojections)--\@ref(fig:fig-DDMhcrPhase);
Table \@ref(tab:tab-omStats)).

```{r fig-DDMprojections, fig.cap = capDDMprojections}
capDDMprojections <- paste0(
  "Simulation projections under the \\emph{SISCAH-DDM} operating model. ",
  "Top: aggregate spawning biomass (kt) with 95\\% envelope (grey) and ",
  "median (black line). Horizontal reference lines show $B_0$ (dotted), ",
  "$B_{ref}$ (dashed blue), and LRP (dashed red). ",
  "Middle: commercial catch by fleet. Bottom: SOB/FSC catch. ",
  "Vertical dashed line marks the start of the projection period (2024).")
plotSimProj(obj = simDDM)
```

```{r fig-DDMretro, fig.cap = capDDMretro}
capDDMretro <- paste0(
  "Retrospective spawning biomass fits under the \\emph{SISCAH-DDM} ",
  "operating model for a single representative replicate. Red line: ",
  "operating model true SSB. Blue line: final \\emph{SISCAH-DIM} ",
  "assessment estimate. Grey lines: earlier assessment estimates. ",
  "Points show scaled survey indices. Vertical dashed line marks ",
  "the start of the projection period.")
plotRetroFits(obj = simDDM, iRep = 1)
```

```{r fig-DDMhcrPhase, fig.cap = capDDMhcrPhase, fig.asp = 1.1}
capDDMhcrPhase <- paste0(
  "HCR scatter plot under the \\emph{SISCAH-DDM} operating model. ",
  "Top: effective harvest rate ($U = \\text{TAC}/B$) vs true ",
  "spawning biomass $B$ (kt). Bottom: TAC (kt) vs $B$. ",
  "Solid line: HCR curve ($B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$). ",
  "Grey points: simulated outcomes across projection years and replicates. ",
  "Dashed line indicates $B_{ref}$ (vertical); dotted line indicates ",
  "$U_{ref}$ (horizontal).")
plotHCRScatter(obj = simDDM)
```

## Robustness test: *SISCAH-1S-Pred* operating model

### RP performance

Under the *SISCAH-1S-Pred* operating model, the RP produces
lower catches across roe fisheries and FSC compared to the
DDM reference case. Biomass starts lower and declines toward
the $B_{ref} \approx B_{MSY|DDM}$ level, reflecting that the
predation mortality model produces a lower equilibrium 
unfished biomass ($B_0 \approx 26.2$ kt) than the DDM model 
($B_0 \approx 42$ kt). Initial TACs are set quite high given
the large recent spawn index from Stat Area 24, which is 
interpreted as a large outlier by the *SISCAH-1S-Pred* OM.
Future catches decline after 2024 with the simulated indices,
which vary around the OM spawning biomass just above the
$B_{ref}$ level. Biomass remains above the LRP 100\%
of the time (pLRP), but MAC10 declines to approximately
1,600 t and the fishery is open in 8 of 10 years
(Figures \@ref(fig:fig-1Sprojections)--\@ref(fig:fig-1Sretro);
Table \@ref(tab:tab-omStats)).

The *SISCAH-DIM* assessment model used in the RP has more
flexibility to chase high data points than would be ideal,
leading to over-estimates of biomass for most of the
projection period. This assessment model mis-specification is
more problematic under the predation OM than under the DDM
OM, as the DIM formulation lacks any structural constraint
on $M$, which allows it to track large spawn indices
towards the end of the historical period. 

Assessment errors translate to some over-harvesting near the
$B_{ref}$ level (Figure \@ref(fig:fig-1ShcrPhase)), where the 
assessment model over-estimates biomass and opens the fishery 
when the true biomass is below the minimum escapement threshold. 
Despite this, a substantial proportion of simulated outcomes 
result in fishery closures even when true biomass exceeds $B_{ref}$,
consistent with the lower equilibrium biomass under the
predation OM.

```{r fig-1Sprojections, fig.cap = cap1Sprojections, fig.asp = 1.0}
cap1Sprojections <- paste0(
  "Simulation projections under the \\emph{SISCAH-1S-Pred} ",
  "operating model. Top: spawning biomass (kt) with 95\\% ",
  "envelope (grey) and median (black). Horizontal reference ",
  "lines show $B_0$ (dotted), LRP (dashed red), and $B_{ref}$ ",
  "(dashed green). Middle: commercial catch by fleet. Bottom: ",
  "SOB/FSC catch.")
knitr::include_graphics(here::here(
  "Models/Sims/sim_1SpredMOM_minEMP_full",
  "simReport_files/figure-html",
  "plotMPSummaryArea-1.png"))
```

```{r fig-1Sretro, fig.cap = cap1Sretro}
cap1Sretro <- paste0(
  "Retrospective spawning biomass fits under the ",
  "\\emph{SISCAH-1S-Pred} operating model for a single ",
  "representative replicate. Red line: operating model ",
  "true SSB. Blue line: final \\emph{SISCAH-DIM} assessment ",
  "estimate. Grey lines: earlier assessment estimates. ",
  "Points show scaled survey indices. Vertical dashed line ",
  "marks the start of the projection period.")
plotRetroSBagg(obj = sim1S, iRep = 1)
```

```{r fig-1ShcrPhase, fig.cap = cap1ShcrPhase, fig.asp = 1.1}
cap1ShcrPhase <- paste0(
  "HCR scatter plot under the \\emph{SISCAH-1S-Pred} operating model. ",
  "Top: effective harvest rate ($U = \\text{TAC}/B$) vs true ",
  "spawning biomass $B$ (kt). Bottom: TAC (kt) vs $B$. ",
  "Solid line: HCR curve ($B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$). ",
  "Grey points: simulated outcomes across projection years and replicates. ",
  "Dashed line indicates $B_{ref}$ (vertical); dotted line indicates ",
  "$U_{ref}$ (horizontal).")
plotHCRScatter(obj = sim1S)
```


## Robustness test: *SISCAH-3S-Pred* operating model

### Aggregate performance

Under the *SISCAH-3S-Pred* operating model, the aggregate
WCVI biomass is near the minimum escapement reference point
($B_{ref} \approx B_{MSY|DDM} \approx 17.35$ kt) at the
start
of the projection period. The aggregate unfished biomass
under this OM is approximately 17.1 kt, meaning that the
$B_{ref}$ threshold is essentially at the unfished level.
As a result, the fishery is open in only 6 of 10
projection years and catches are very small when the
fishery is open. Aggregate pLRP remains at 100\%
because the LRP ($0.3 B_0 \approx 5.1$ kt) is well
below the operating biomass, but MAC10 is only
approximately 330 t and p650 is 21\%
(Table \@ref(tab:tab-omStats)).

The largest catches occur in the first two projection
years, driven by high recent spawn index values. After
those initial years, the fishery remains mostly closed
as the assessment model adjusts to the low biomass
level.

As with the *SISCAH-1S-Pred* OM, the DIM assessment model
has more flexibility to track high data points, leading to
some over-estimates. However, the flat biomass trajectory in
the projection period limits the impact of these
over-estimates
(Figures \@ref(fig:fig-3Sprojections)--\@ref(fig:fig-3ShcrPhase)).

```{r fig-3Sprojections, fig.cap = cap3Sprojections, fig.asp = 1.0}
cap3Sprojections <- paste0(
  "Aggregate simulation projections under the ",
  "\\emph{SISCAH-3S-Pred} operating model (SI distribution). ",
  "Top: spawning biomass (kt) with aggregate envelope ",
  "(grey) and per-Stat Area median lines (coloured). ",
  "Middle: commercial catch by Stat Area. Bottom: ",
  "SOB/FSC catch by Stat Area. Horizontal reference ",
  "lines show $B_0$ (dotted), LRP (dashed red), and ",
  "$B_{ref}$ (dashed green).")
plotMPSummary(
  obj       = sim3S_MP1,
  aggregate = TRUE)
```

```{r fig-3SprojByArea, fig.cap = cap3SprojByArea, fig.asp = 1.0}
cap3SprojByArea <- paste0(
  "Per-Stat Area projections under the ",
  "\\emph{SISCAH-3S-Pred} operating model (SI distribution). ",
  "Columns show Stat Areas 25, 24, and 23. Rows show ",
  "spawning biomass (kt), commercial catch by fleet (kt), ",
  "and SOB/FSC catch (kt). Reference lines in SSB panels ",
  "show per-area $B_0$ (dotted) and LRP (dashed red).")
plotMPSummary(
  obj       = sim3S_MP1,
  aggregate = FALSE)
```

```{r fig-3Sretro, fig.cap = cap3Sretro}
cap3Sretro <- paste0(
  "Retrospective spawning biomass fits under the \\emph{SISCAH-3S-Pred} ",
  "operating model for a single representative replicate. Red line: ",
  "operating model true SSB. Blue line: final \\emph{SISCAH-DIM} ",
  "assessment estimate. Grey lines: earlier assessment estimates. ",
  "Points show scaled survey indices. Vertical dashed line marks ",
  "the start of the projection period.")
plotRetroSBagg(obj = sim3S_MP1, iRep = 1)
```

```{r fig-3ShcrPhase, fig.cap = cap3ShcrPhase, fig.asp = 1.1}
cap3ShcrPhase <- paste0(
  "HCR scatter plot under the \\emph{SISCAH-3S-Pred} operating model. ",
  "Top: effective harvest rate ($U = \\text{TAC}/B$) vs true ",
  "spawning biomass $B$ (kt). Bottom: TAC (kt) vs $B$. ",
  "Solid line: HCR curve ($B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$). ",
  "Grey points: simulated outcomes across projection years and replicates. ",
  "Dashed line indicates $B_{ref}$ (vertical); dotted line indicates ",
  "$U_{ref}$ (horizontal).")
plotHCRScatter(obj = sim3S_MP1)
```

### Spatial TAC distribution

Three distribution methods were tested for distributing the
aggregate TAC among Stat Areas (Section \@ref(sec:distribution)).
The 2024 distribution proportions based on spawn indices are
approximately 5\%, 38\%, and 57\% for Stat Areas 25, 24, and 23,
respectively, while long-term average proportions are
approximately 11\%, 31\%, and 58\%. Catch-based proportions
are approximately 25\%-30\% for Stat Areas 25 and 24, and
38\%-47\% for Stat Area 23
(Table \@ref(tab:tab-allocProportions)).

```{r tab-allocProportions}
makeAllocTable(mp1 = sim3S_MP1, mp2 = sim3S_MP2, mp3 = sim3S_MP3)
```

### Performance by Stat Area

The probability of low biomass (biomass below the historical
minimum) is very low across all Stat Areas and distribution
methods, ranging from 0\% to 0.2\%. This is because catches
are negligible and biomass performance is driven almost
entirely by natural and predation mortality rather than
fishing.

The probability of low catch (catch below the historical
minimum) is high for all Stat Areas and distribution methods,
ranging from 71\% to 100\%. This reflects the near-permanent
fishery closure under the *SISCAH-3S-Pred* OM.

Despite the negligible catches, Stat Area-level metrics
are reported for completeness and to confirm that no
distribution method introduces biomass risk to individual
Stat Areas. There is very little difference among
distribution methods or among Stat Areas in either
metric. Given that catches are close to zero, the method
used to distribute them has negligible impact on
outcomes
(Tables \@ref(tab:tab-perfBiomass)--\@ref(tab:tab-perfCatch)).

```{r tab-perfBiomass}
perfTbls <- makePerfTables()
perfTbls$biomass
```

```{r tab-perfCatch}
perfTbls$catch
```

## Aggregate performance comparison

Table \@ref(tab:tab-omStats) summarises aggregate
performance across all three operating models.

```{r tab-omStats}
makeOMStatsTable()
```
