# Results

Results are presented for each operating model in turn,
starting with the *SISCAH-DDM* operating model where the MP
assumptions are well matched, followed by the
*SISCAH-1S-Pred* and *SISCAH-3S-Pred* robustness tests.

## Reference case: *SISCAH-DDM* operating model

### Biological reference points

Under the *SISCAH-DDM* operating model, the yield curve
produces an unfished biomass of approximately 42 kt,
$B_{MSY} \approx 17.35$ kt, a limit reference point of
$0.3 B_0 \approx 13.5$ kt, and a maximum sustainable yield
of approximately 1.6 kt. The LRP and $B_{MSY}$ are close
together, meaning that the stock transitions relatively
quickly from a productive state to one requiring closure.

### MP performance

When the MP is applied to the *SISCAH-DDM* operating model,
performance is consistent with expectations given that the
assessment model and OM share the same structural assumptions.
The assessment model (*SISCAH-DIM*) estimates biomass
reasonably well, with no major evidence of bias during the
projection period. Median projected biomass remains well above
$B_{ref} = B_{MSY|DDM}$, and biomass is maintained above
the LRP ($0.3 B_0$) approximately 96\% of the time,
exceeding the 75\% conservation objective. Commercial catches
(split among roe fisheries) and SOK/FSC catches are at
levels similar to the historical average. The effective
harvest rates applied during the projection period are
consistent with the intended HCR.

```{r fig-DDMprojections, fig.cap = capDDMprojections}
capDDMprojections <- paste0(
  "Simulation projections under the \\emph{SISCAH-DDM} operating model. ",
  "Top: aggregate spawning biomass (kt) with 95\\% envelope (grey) and ",
  "median (black line). Horizontal reference lines show $B_0$ (dotted), ",
  "$B_{ref}$ (dashed blue), and LRP (dashed red). ",
  "Middle: commercial catch by fleet. Bottom: SOK/FSC catch. ",
  "Vertical dashed line marks the start of the projection period (2024).")
plotSimProj(obj = simDDM)
```

```{r fig-DDMretro, fig.cap = capDDMretro}
capDDMretro <- paste0(
  "Retrospective spawning biomass fits under the \\emph{SISCAH-DDM} ",
  "operating model for a single representative replicate. Red line: ",
  "operating model true SSB. Blue line: final \\emph{SISCAH-DIM} ",
  "assessment estimate. Grey lines: earlier assessment estimates. ",
  "Points show scaled survey indices. Vertical dashed line marks ",
  "the start of the projection period.")
plotRetroFits(obj = simDDM, iRep = 1)
```

```{r fig-DDMhcrPhase, fig.cap = capDDMhcrPhase, fig.asp = 1.1}
capDDMhcrPhase <- paste0(
  "HCR scatter plot under the \\emph{SISCAH-DDM} operating model. ",
  "Top: effective harvest rate ($U = \\text{TAC}/B$) vs true ",
  "spawning biomass $B$ (kt). Bottom: TAC (kt) vs $B$. ",
  "Solid line: HCR curve ($B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$). ",
  "Grey points: simulated outcomes across projection years and replicates. ",
  "Dashed line indicates $B_{ref}$ (vertical); dotted line indicates ",
  "$U_{ref}$ (horizontal).")
plotHCRScatter(obj = simDDM)
```

## Robustness test: *SISCAH-1S-Pred* operating model

### MP performance

Under the *SISCAH-1S-Pred* operating model, the MP produces
lower catches across roe fisheries and FSC compared to the
DDM reference case. Biomass starts lower and declines toward
the $B_{ref} = B_{MSY|DDM}$ level, reflecting that the
predation mortality model produces a lower equilibrium biomass
($B_0 \approx 26.2$ kt) than the DDM model ($B_0 \approx
42$ kt). Large recent spawn indices drive initial catches
higher, but catches decline as the assessment model adjusts
to the lower true biomass.

The *SISCAH-DIM* assessment model used in the MP has more
flexibility to chase high data points than would be ideal,
leading to over-estimates of biomass for most of the
projection period. This assessment model mis-specification is
more problematic under the predation OM than under the DDM
OM, as the DIM formulation lacks the structural constraint of
density-dependent mortality. However, the flat biomass and
indices in the projection period reduce the scale of
over-estimates relatively quickly.

Assessment errors translate to some over-harvesting near the
$B_{ref}$ level, where the assessment model over-estimates
biomass and opens the fishery when the true biomass is below
the minimum escapement threshold. Despite this, a
substantial proportion of simulated outcomes result in
fishery closures even when true biomass exceeds $B_{ref}$,
consistent with the lower equilibrium biomass under the
predation OM.

```{r fig-1Sprojections, fig.cap = cap1Sprojections, fig.asp = 1.0}
cap1Sprojections <- paste0(
  "Simulation projections under the \\emph{SISCAH-1S-Pred} ",
  "operating model. Top: spawning biomass (kt) with 95\\% ",
  "envelope (grey) and median (black). Horizontal reference ",
  "lines show $B_0$ (dotted), LRP (dashed red), and $B_{ref}$ ",
  "(dashed green). Middle: commercial catch by fleet. Bottom: ",
  "SOK/FSC catch.")
knitr::include_graphics(here::here(
  "Models/Sims/sim_1SpredMOM_minEMP_full",
  "simReport_files/figure-html",
  "plotMPSummaryArea-1.png"))
```

```{r fig-1Sretro, fig.cap = cap1Sretro}
cap1Sretro <- paste0(
  "Retrospective spawning biomass fits under the ",
  "\\emph{SISCAH-1S-Pred} operating model for a single ",
  "representative replicate. Red line: operating model ",
  "true SSB. Blue line: final \\emph{SISCAH-DIM} assessment ",
  "estimate. Grey lines: earlier assessment estimates. ",
  "Points show scaled survey indices. Vertical dashed line ",
  "marks the start of the projection period.")
knitr::include_graphics(here::here(
  "Models/Sims/sim_1SpredMOM_minEMP_full",
  "simReport_files/figure-html",
  "plotRetroSBagg-1.png"))
```

```{r fig-1ShcrPhase, fig.cap = cap1ShcrPhase, fig.asp = 1.1}
cap1ShcrPhase <- paste0(
  "HCR scatter plot under the \\emph{SISCAH-1S-Pred} operating model. ",
  "Top: effective harvest rate ($U = \\text{TAC}/B$) vs true ",
  "spawning biomass $B$ (kt). Bottom: TAC (kt) vs $B$. ",
  "Solid line: HCR curve ($B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$). ",
  "Grey points: simulated outcomes across projection years and replicates. ",
  "Dashed line indicates $B_{ref}$ (vertical); dotted line indicates ",
  "$U_{ref}$ (horizontal).")
plotHCRScatter(obj = sim1S)
```

### Comparison of single-stock OM performance

Table \@ref(tab:tab-omStats) summarises aggregate
performance under both single-stock operating models.

```{r tab-omStats}
makeOMStatsTable()
```

## Robustness test: *SISCAH-3S-Pred* operating model

### Aggregate performance

Under the *SISCAH-3S-Pred* operating model, the aggregate
WCVI biomass is near the minimum escapement reference point
($B_{ref} = B_{MSY|DDM} \approx 17.35$ kt) at the start
of the projection period. The aggregate unfished biomass
under this OM is approximately 17.1 kt, meaning that the
$B_{ref}$ threshold is essentially at the unfished level.
As a result, the fishery is closed more than 50\% of the time,
and catches are very small when the fishery is open.

The largest catches occur in the first two projection years,
driven by high recent spawn index values. After those initial
years, the fishery remains mostly closed as the assessment
model adjusts to the low biomass level.

As with the *SISCAH-1S-Pred* OM, the DIM assessment model
has more flexibility to track high data points, leading to
some over-estimates. However, the flat biomass trajectory in
the projection period limits the impact of these over-estimates.

```{r fig-3Sprojections, fig.cap = cap3Sprojections, fig.asp = 1.0}
cap3Sprojections <- paste0(
  "Aggregate simulation projections under the ",
  "\\emph{SISCAH-3S-Pred} operating model (SI distribution). ",
  "Top: spawning biomass (kt) with aggregate envelope ",
  "(grey) and per-Stat Area median lines (coloured). ",
  "Middle: commercial catch by Stat Area. Bottom: ",
  "SOK/FSC catch by Stat Area. Horizontal reference ",
  "lines show $B_0$ (dotted), LRP (dashed red), and ",
  "$B_{ref}$ (dashed green).")
plotMPSummary(
  obj       = sim3S_MP1,
  aggregate = TRUE)
```

```{r fig-3SprojByArea, fig.cap = cap3SprojByArea, fig.asp = 1.0}
cap3SprojByArea <- paste0(
  "Per-Stat Area projections under the ",
  "\\emph{SISCAH-3S-Pred} operating model (SI distribution). ",
  "Columns show Stat Areas 25, 24, and 23. Rows show ",
  "spawning biomass (kt), commercial catch by fleet (kt), ",
  "and SOK/FSC catch (kt). Reference lines in SSB panels ",
  "show per-area $B_0$ (dotted) and LRP (dashed red).")
plotMPSummary(
  obj       = sim3S_MP1,
  aggregate = FALSE)
```

```{r fig-3Sretro, fig.cap = cap3Sretro}
cap3Sretro <- paste0(
  "Retrospective spawning biomass fits under the \\emph{SISCAH-3S-Pred} ",
  "operating model for a single representative replicate. Red line: ",
  "operating model true SSB. Blue line: final \\emph{SISCAH-DIM} ",
  "assessment estimate. Grey lines: earlier assessment estimates. ",
  "Points show scaled survey indices. Vertical dashed line marks ",
  "the start of the projection period.")
plotRetroSBagg(obj = sim3S_MP1, iRep = 1)
```

```{r fig-3ShcrPhase, fig.cap = cap3ShcrPhase, fig.asp = 1.1}
cap3ShcrPhase <- paste0(
  "HCR scatter plot under the \\emph{SISCAH-3S-Pred} operating model. ",
  "Top: effective harvest rate ($U = \\text{TAC}/B$) vs true ",
  "spawning biomass $B$ (kt). Bottom: TAC (kt) vs $B$. ",
  "Solid line: HCR curve ($B_{ref} = 17.35$ kt, $U_{ref} = 8.47\\%$). ",
  "Grey points: simulated outcomes across projection years and replicates. ",
  "Dashed line indicates $B_{ref}$ (vertical); dotted line indicates ",
  "$U_{ref}$ (horizontal).")
plotHCRScatter(obj = sim3S_MP1)
```

### Spatial TAC distribution

Three distribution methods were tested for distributing the
aggregate TAC among Stat Areas (Section \@ref(sec:allocation)).
The 2024 distribution proportions based on spawn indices are
approximately 5\%, 38\%, and 57\% for Stat Areas 25, 24, and 23,
respectively, while long-term average proportions are
approximately 11\%, 31\%, and 58\%. Catch-based proportions
are approximately 25\%-30\% for Stat Areas 25 and 24, and
38\%-47\% for Stat Area 23
(Table \@ref(tab:tab-allocProportions)).

```{r tab-allocProportions}
makeAllocTable(mp1 = sim3S_MP1, mp2 = sim3S_MP2, mp3 = sim3S_MP3)
```

### Performance by Stat Area

The probability of low biomass (biomass below the historical
minimum) is very low across all Stat Areas and distribution
methods, ranging from 0\% to 0.2\%. This is because catches
are negligible and biomass performance is driven almost
entirely by natural and predation mortality rather than
fishing.

The probability of low catch (catch below the historical
minimum) is high for all Stat Areas and distribution methods,
ranging from 71\% to 100\%. This reflects the near-permanent
fishery closure under the *SISCAH-3S-Pred* OM.

There is very little difference among distribution methods
or among Stat Areas in either performance metric. Given that
catches are close to zero, the method used to distribute them
has negligible impact on outcomes.

```{r tab-perfBiomass}
perfTbls <- makePerfTables()
perfTbls$biomass
```

```{r tab-perfCatch}
perfTbls$catch
```
