
\clearpage

```{=latex}
% Do not delete this

\appendixpageoff
\appendixtitleoff

\begin{appendices}
\counterwithin{figure}{section}
\counterwithin{table}{section}
```

# SISCAH-3S-Pred predation mortality models {#app:threeStockPred}

This appendix briefly describes the *SISCAH-3S-Pred*
model. The *3S-Pred* model is fitted to WCVI Herring
spawn index, catch, and catch-at-age data disaggregated
to the Stat Area level, as well as coast-wide predator
consumption estimates. The model is described over three
tables, including notation
(Table \ref{tab:SISCAnotation}), model parameters and
process model equations
(Table \ref{tab:SISCAprocModelEqns}), and statistical
model equations broken into observation models, parameter
priors, and the final model objective function
(Table \ref{tab:SISCAstatModelEqns}). Other than the two
changes described below, the model is the same as
*SISCAH-1S-Pred*; readers are referred to
@doherty2024predation for more information.

There are two main changes in the specification and data
used for the *SISCAH-3S-Pred* model from the
*SISCAH-1S-Pred* model, and both are related to the way
predators are treated. First, the Humpback Whale predator
consumption is split into four seasonal feeding groups,
rather than the two seasonal groups used in the original
publication where *SISCAH-1S-Pred* is developed
[@doherty2024predation]. Seasonal feeding groups are used
to bring the relative consumption among seasons more in
line with observations of Humpback abundance in the Juan
de Fuca strait during survey effort
[@mcmillan2022hbSeasonalAbundance].

The second change is that bio-energetic predator
consumption estimates are provided at a coastwide level,
rather than the same Stat Area level as the herring
populations. Finer spatial detail on bio-energetic
estimates is not possible, as the consumption is estimated
from models of predator abundance/biomass, and there are
no data available to estimate predator populations at a
finer scale than the WCVI coast. Therefore, predator
consumption is provided to *SISCAH-3S-Pred* as a mixed
coastwide consumption, which is then split among the three
Stat Areas in proportion to the vulnerable biomass
(Table \@ref(tab:SISCAprocModelEqns), M.1--M.3). This
approach assumes that inshore predators split foraging
effort among Stat Areas in proportion to prey
availability, and offshore predators randomly remove
herring from the mixed feeding aggregation.

\clearpage


## Tables

```{r tableCapsA, echo = FALSE, include = FALSE, warning = FALSE}
notationTableCap <- "Notation used in the SISCAH-3S-Pred stock assessment model including predation mortality."

procModelEqnsCap  <- "Process model equations for the SISCAH-3S-Pred stock assessment model including predation mortality."

statModelEqnsCap   <- "Data likelihoods, model prior density functions, and the final objective function for the SISCAH-3S-Pred stock assessment model including predation mortality. $\\mathbf{1}(X)$ is the indicator function that takes value 1 when the statement $X$ is true, and $0$ otherwise."
```

```{r SISCAnotation, echo = FALSE, message = FALSE, warnings = FALSE}

options(knitr.kable.NA = "")

notationTable <- tibble::tribble( 
    ~Symbol,              ~Value,             ~Description,
    "$T$",                "$73$",             "Total number of time steps 1951 - 2023",
    NA,NA,NA,
    "$A$",                "$10$",             "Plus group age-class",
    NA,NA,NA,
    "$t$",                "$1,2,\\dots,T$",   "Time step",
    NA,NA,NA,
    "$a$",                "$1,2,\\dots,A$",   "Age-class index",
    NA,NA,NA,
    "$p$",                "$1,2,3$",          "stock index for (1) PFMA25, (2) PFMA24, and (3) PFMA23.",
    NA,NA,NA,
    "$g$",                "$1,2,\\dots,14$",  "Gear index for (1) reduction, (2) seine-roe, and (3) gillnet fisheries,",
    NA, NA,                                   "(4) Surface and (5) dive spawn survey indices, (6) the closed", 
    NA, NA,                                   "pond SOKB fishery, (7) Hake less than 50 cm, (8) Hake greater",
    NA, NA,                                   "than 50 cm, (9) Harbor Seals, (10) Stellar Sea Lions,",
    NA, NA,                                   "(11) Winter Humpback Whale, (12) Spring Humpback Whale,",
    NA, NA,                                   "(13) Summer Humpback Whale, and (14) Fall Humpback Whale.",
    NA,NA,NA,
    "$B_{0,p}$",            NA,               "Unfished spawning stock biomass in area $p$",
    NA,NA,NA,
    "$\\mbox{eggs}_{0,p}$",  NA,              "Equilibirum unfished egg production in area $p$",
    NA,NA,NA,
    "$\\mbox{eggs}_{p,t}$", NA,               "The number of eggs released by area $p$ spawners in year $t$",
    NA,NA,NA,
    "$h_p$",                NA,               "Beverton-Holt stock-recruitment steepness in area $p$",
    NA,NA,NA,
    "$R_{0,p}$",            NA,               "Unfished equilibrium recruitment in area $p$",
    NA,NA,NA,
    "$R^{init}_{p}$",         NA,             "Initial recruitment in area $p$",
    NA,NA,NA,
    "$\\bar{R_p}$",         NA,               "Average recruitment in area $p$",
    NA,NA,NA,
    "$\\omega^{init}_{a,p}$",NA,              "Initial recruitment log-deviations",
    NA,NA,NA,
    "$S_{a,p}$",            NA,               "Unfished equilibrium survivorship-at-age in area $p$",
    NA,NA,NA,
    "$\\beta_1,\\beta_2$","$20, 9.84$",       "Beta prior parameters for stock-recruit steepness",
    NA,NA,NA,
    "$\\phi_{0,p}$",        NA,               "Unfished equilibrium spawning biomass per recruit in area $p$",
    NA,NA,NA,
    "$\\omega_{p,t}$",      NA,               "Annual recruitment process error log-deviations in area $p$",
    NA,NA,NA,
    "$\\sigma_{R}$",      "$0.8$",            "Standard error of $\\omega_{p,t}$ recruitment deviations",
    NA,NA,NA,
    "$q_{s,p}$",            NA,               "Catchability coefficient for the surface survey design in area $p$",
    NA,NA,NA,
    "$q_{d}$",            "$1$",              "Catchability coefficient for the dive survey design",
    NA,NA,NA,
    "$q'_{p,t}$",           NA,               "Annual convex-combination of survey catchabilities in area $p$",
    NA,NA,NA,
    "$q^{pred}_{p,g,t}$",     NA,             "Per-capita predation rate for predator $g$ in area $p$",
    NA,NA,NA,
    "$E_{g,t}$",     NA,                      "Effort (abundance/biomass) for predator $g > 6$",
    NA,NA,NA,
    "$\\epsilon^{pred}_{p,g,t}$",     NA,       "Annual random walk $\\log$-deviations in per-capita",
    NA,NA,                                    "predation rate for predator $g$ in area $p$",
    NA,NA,NA,
    "$\\sigma^{pred}$",   "$0.5$",            "Standard deviation for simple random walk in",
    NA,NA,                                    "$\\log$ per-capita predation rate.",
    NA,NA,NA,
    "$\\mu_{q_s}$",      "$0.5$",             "Surface survey catchability $\\log$-Normal prior mean",
    NA,NA,NA,
    "$\\tau_{q_s}$",     "$0.5$",             "Surface survey catchability $\\log$-Normal prior standard deviation",
    NA,NA,NA,
    "$M_{p,t_{0}}$",        NA,               "Initial natural mortality rate in area $p$",
    NA,NA,NA,
    "$\\epsilon^{(M)}_{p,t}$",    NA,         "Annual $\\log$-deviations in natural mortality rate in area $p$",
    NA,NA,NA,
    "$\\sigma_{M}$",      "$.1$",             "Standard error in annual natural mortality log-deviations",
    NA,NA,NA,
    "$M_{a,p,t}$",          NA,               "Annual natural mortality rate for age $a$ in area $p$", 
    NA,NA,NA,
    "$w_{a,p,t}$",          NA,               "Annual average weight-at-age observations in area $p$",
    NA,NA,NA,
    "$m_a$",              NA,                 "Proportion mature at age $a$",
    NA,NA,NA,
    "$s^{50}_{p,g}$",       NA,               "Age-at-50\\% selectivity for gear/predator $g$ in area $p$",
    NA,NA,NA,
    "$s^{Step}_{p,g}$",     NA,               "Difference between age-at-50\\% and age-at-95\\% selectivity for",
    NA,                   NA,                 "gear/predator $g$",
    NA,NA,NA,
    "$s_{a,p,g}$",        NA,                 "Selectivity-at-age $a$ for gear/predator $g$",
    NA,NA,NA,
    "$\\delta_g$",        NA,                 "Fractional time-step at which catch/consumption from",
    NA,NA,                                    "fishery/predator $g$ is removed from the population",
    NA,NA,NA,
    "$R_{p,t}$",              NA,             "Estimated Age-1 recruitment in area $p$ at time $t$",
    NA,NA,NA,
    "$\\overline{R}_{p,t}$",       NA,        "Expected (deterministic) age-1 recruitment in area $p$",
    NA,       NA,                             "from a Beverton-Holt stock-recruit relationship",
    NA,NA,NA,
    "$N_{a,p,t + \\delta_g}$",NA,             "Total numbers-at-age $a$ in area $p$ at fractional time-step $t + \\delta_g$",
    NA,NA,NA,
    "$N_{a,p,g,t + \\delta_g}$",NA,           "Total numbers-at-age $a$ in area $p$ vulnerable to fishery/predator $g$x",
    NA,                   NA,                 "at fractional time-step $t + \\delta_g$",
    NA,NA,NA,
    "$N^{spawn}_{a,p,t}$",          NA,       "Total numbers-at-age $a$ in area $p$ in year $t$ at spawning time",
    NA,NA,NA,
    "$B_{p,t}$",            NA,               "Spawning biomass in area $p$ during year $t$",
    NA,NA,NA,
    "$C_{a,p,g,t}$",        NA,               "Model estimate of catch-/consumption-at-age $a$ in",
    NA,NA,                                    "numbers by gear/predator $g$ in year $t$ in area $p$",
    NA,NA,NA,
    "$C'_{a,p,g,t}$",       NA,               "Model estimate of catch-/consumption-at-age $a$ in biomass",
    NA,NA,                                    "units by gear/predator $g$ in area $p$, year $t$",
    NA,NA,NA,
    "$\\hat{C}_{p,g,t}$",   NA,               "Model estimate of catch-/consumption in biomass units by",
    NA,NA,                                    "gear/predator $g$ in area $p$, year $t$",
    NA,NA,NA,
    "$C_{p,g,t}$",          NA,               "Input catch data or bio-energetic consumption estimates",
    NA,NA,                                    "in biomass units by gear/predator $g$ in area $p$, year $t$",
    NA,NA,NA,
    "$\\hat{C}_{p,g,t}$",   NA,               "Model estimate of catch data or consumption in biomass units by",
    NA,NA,                                    "gear/predator $g$ in area $p$, year $t$",
    NA,NA,NA,
    "$\\tau^C_g$",        NA,                 "$\\log$-Normal standard deviation of residual errors between",
    NA,                   NA,                 "consumption estimates from bio-energetic model and SISCAH-3S-Pred",
    NA,NA,NA,
    "$U_{p,g,t}$",          NA,               "Harvest rate of herring in area $p$ by gear $g$ in year $t$",
    NA,NA,NA,
    "$K_{p,t}$",            NA,               "Total landed weight of Spawn-on-Kelp/Bough product at",
    NA,NA,                                    "time $t$ in area $p$",
    NA,NA,NA,
    "$P_{p,t}$",            NA,               "Ponded whole-fish biomass for Spawn-on-Kelp/Bough",
    NA,NA,                                    "fishery in area $p$, year $t$",
    NA,NA,NA,
    "$\\Psi_{t}$",        NA,                 "Conversion factor from ponded fish to landed SOKB",
    NA,NA,NA,
    "$\\mathfrak{F}_a$",    NA,               "Average fecundity at age $a$ of female herring",
    NA,NA,                                    "(eggs per gram of spawning biomass)",
    NA,NA,NA,
    "$p_{mat,p,t}$",          NA,             "Proportion of herring that are mature at time $t$ in area $p$",
    NA,NA,NA,
    "$p_{fem,p,t}$",       "$0.5$",           "Proportion of herring that are female at time $t$ in area $p$",
    NA,NA,NA,
    "$p_{eff,p,t}$",       "$0.35$",          "Proportion of herring at time $t$ that will spawn in the closed pond in area $p$",
    NA,NA,NA,
    "$\\gamma_g$",       "$0.0024$",          "Conversion factor from eggs to SOKB product",
    NA,NA,NA,
    "$I_{p,t}$",           NA,                "Observed blended spawn index at time $t$ in area $p$",
    NA,NA,NA,
    "$\\hat{I}_{p,t}$",     NA,               "Expected blended spawn index at time $t$ in area $p$",
    NA,NA,NA,
    "$\\eta_{p,t}$",        NA,               "Proportion of annual spawn survey index",
    NA,NA,                                    "observed in the surface survey design",
    NA,NA,NA,
    "$\\tau^{I}_{p,g}$",    NA,               "Surface ($g = s$) or dive ($g = d$) component of",
    NA,NA,                                    "blended spawn index $\\log$ residual standard error in area $p$",
    NA,NA,NA,
    "$\\tau^{I}_{p,t}$",    NA,               "Yearly blended spawn-index $\\log$ residual standard error in area $p$",
    NA,NA,NA,
    "$u_{a,p,g,t}$",        NA,               "Observed proportion of catch-at-age $a$ by gear $g$",
    NA,NA,                                    "at time $t$ in area $p$",
    NA,NA,NA,
    "$\\hat{u}_{a,p,g,t}$", NA,               "Expected proportion of catch-at-age $a$ by gear $g$",
    NA,NA,                                    "at time $t$ in area $p$",
    NA,NA,NA,
    "$\\mathfrak{B}_{p,g,t}$",NA,             "Total number of age classes in year $t$ in area $p$ with",
    NA,                     NA,               "proportion of catch-at-age observations above 2\\%",
    NA,NA,                                    "of the total sample",
    NA,NA,NA,
    "$\\hat{\\tau}^{age}_{p,g}$", NA,         "Conditional maximum likelihood estimate",
    NA,NA,                                    "of age composition sampling error",
    NA,NA,NA,
    "$m_{M}$",            "$0.45$",           "Prior mean initial natural mortality",
    NA,NA,NA,
    "$s_{M}$",            "$0.4$",            "$\\log$-scale standard deviation on initial mortality", 
    NA,NA,NA,
    "$m^{s^{50}}_{g}$",   NA,                 "Population mean age-at-50\\% selectivity for gear $g$",
    NA,NA,NA,
    "$s^{s^{50}}_{g}$",   "$0.3$",            "$\\log$-deviation of $s^{50}_g$ from $\\mu_{s^{50},g}$", 
    NA,NA,NA,
    "$m^{s^{Step}}_{g}$", NA,                 "Population mean step from age-at-50\\% to age-at-95\\%",
    NA,NA,                                    "selectivity for gear $g$",
    NA,NA,NA,
    "$s^{s^{Step}}_{g}$", "$0.3$",            "$\\log$-deviation of $s^{Step}_g$ from $\\mu_{s^{Step},g}$", 
    NA,NA,NA,
    "$\\rho_g$",          NA,                 "Correlation-at-lag-1 in age composition residuals",
    NA,NA,NA,
    "$\\mathfrak{C}$",    NA,                 "Lag-1 correlation matrix for age composition residuals",
    NA,NA,NA,
    "$\\mathfrak{K}$",    NA,                 "Dimension transformation matrix for age composition",
    NA,NA,                                    "logistic normal likelihood",
    NA,NA,NA,
    "$\\iota_{p,g,t}$",     NA,               "Centred logistic normal age-composition $\\log$-residuals",
    NA,NA,                                    " for gear $g$ at time step $t$ in area $p$",

)



kable(  notationTable, escape = FALSE,
        longtable = TRUE,
        booktabs = TRUE, 
        format = kable_format,
        # linesep = "\\addlinespace",
        caption = notationTableCap,
        align = c("c","c","l")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 10) 
  #kable_styling(  latex_options = c("hold_position", "scale_down") )
                  #bootstrap_options = c("striped", "hover","scale_down"))
                  #font_size = 10 )


```

\clearpage

\renewcommand{\arraystretch}{2}

```{r SISCAprocModelEqns, echo = FALSE, messages = FALSE, warnings = FALSE}

procModelEqns  <- read.csv("data/procModelEqns.csv", header = TRUE, stringsAsFactors = FALSE)

# procModelEqns <- notationTable

colnames(procModelEqns) <- c("No.", "Equation")

kable( procModelEqns, escape = FALSE,
                      booktabs = TRUE,
                      format = kable_format,
                      longtable = TRUE,
                      linesep = "\\addlinespace",
                      caption = procModelEqnsCap,
                      align = c("c","l")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 10) %>%
  kableExtra::group_rows("Model Parameters", 1, 5 ) %>%
  kableExtra::group_rows("Unfished Equilibrium States", 6, 10 ) %>%
  kableExtra::group_rows("Non-equilibrium Initial States", 11, 13 ) %>%
  kableExtra::group_rows("Natural, Fishing, and Total Mortality", 14, 17 ) %>%
  kableExtra::group_rows("Catch from discrete fisheries (g = 1,2,3)", 18, 26 ) %>%
  kableExtra::group_rows("Predator consumption (g > 6)", 27, 29 ) %>%
  kableExtra::group_rows("Fertilised Herring egg removals (g = 6)", 30, 35 ) %>%
  kableExtra::group_rows("Spawning Biomass, Recruitment, and Numbers-at-age", 36, 40 )

```



\clearpage

```{r SISCAstatModelEqns, echo = FALSE, include = TRUE, messages = FALSE, warnings = FALSE}

# statModelEqns  <- read.csv("data/statModelEqns.csv", header = TRUE, stringsAsFactors = FALSE)

statModelEqns <- tibble::tribble( 

  ~No.,        ~ModelEquation,
  # Observation model equations
  # Expected spawn indices
  "(O.1)",      "$\\displaystyle \\hat{I}_{p,t}   = q'_{t} \\cdot B_{p,t}$",
  # Expected age comps
  "(O.2)",      "$\\displaystyle \\hat{u}_{a,p,g,t} = \\frac{ C_{a,p,g,t} } { \\sum_{a'} C_{a',p,g,t}}$",


  # # Now calculate biomass observation resids
  "(L.1)",      "$\\displaystyle z_{1,t} = \\log \\frac{ I_{t} }{ \\hat{I}_{t} }$",
  "(L.2)",      "$\\displaystyle q'_{t} = \\eta_{t} q_{4} + (1 - \\eta_{t}) q_{5}$",
  "(L.3)",      "$\\displaystyle \\tau^{I}_{t} = \\left( \\eta_{t} (\\tau^{I}_{4})^2 + (1 - \\eta_{t}) (\\tau^{I}_{5})^2\\right)^{1/2}$",
  "(L.4)",      "$\\displaystyle Z_{1,t} = \\frac{z_{1,t}}{\\tau^{I}_t} $",
  "(L.5)",      "$\\displaystyle l_{1} = \\frac12 \\sum_t \\left( \\log \\left(2\\pi(\\tau^{I}_t)^2\\right) + Z_{1,t}\\right)  $",

  # Age composition likelihood
  "(A.1)",      "$\\displaystyle \\mathfrak{C}_g = \\left[ \\rho_g^{j - i} \\right]_{i,j}$",
  "(A.2)",      "$\\displaystyle \\mathfrak{K} = \\left[ I_{A-1} \\vert 1 \\right]$",
  "(A.3)",      "$\\displaystyle V_g = \\mathfrak{K} \\cdot C_g \\cdot \\mathfrak{K}^T$",
  "(A.4)",      "$\\displaystyle W_{p,g,t} = \\frac{ \\mbox{mean} ( {n^{Age}_{p,g,t}} ) }{ n^{Age}_{p,g,t} }$",
  "(A.5)",      "$\\displaystyle \\mathfrak{B}_{p,g,t} = \\sum_{a = 1}^A \\mathbf{1}( u_{a,p,g,t} > 0.02)$",
  "(A.6)",      "$\\displaystyle \\vec {\\iota}_{p,g,t} = \\langle log(u_{a,p,g,t} / u_{\\mathfrak{B}_{p,g,t},p,g,t}) - log(\\hat{u}_{a,p,g,t}/\\hat{u}_{\\mathfrak{B}_{p,g,t},p,g,t} \\rangle_{a,p}$",
  "(A.7)",      "$\\displaystyle \\hat{\\tau}^{age}_{g} = \\left( \\frac{ \\sum_{t} \\frac{1}{W_{g,t}^2}(\\vec{\\iota}_{g,t})^T \\cdot V_g^{-1} \\cdot \\vec{\\iota}_{g,t}}{\\sum_{t} \\mathfrak{B}_{g,t} } \\right)^{0.5}$",
  "(A.8)",      "$\\displaystyle l_{2} = \\sum_{g} \\left( \\sum_{a,p,t} \\log u_{a,p,g,t} + \\log \\hat{\\tau}^{age}_{g} \\sum_{p,t} (\\mathfrak{B}_{p,g,t} - 1) + \\frac12 \\sum_t \\log \\vert V_g \\vert + \\sum_{p,t} (\\mathfrak{B}_{p,g,t} - 1)\\log W_{p,g,t} \\right)$",

  # Predator consumption likelihood function
  "(Co.1)",     "$\\displaystyle z_{3,p,t} = \\frac{\\log \\hat{C}_{p,t} - \\log C_{p,t}}{\\tau^C_{p}}$",
  "(Co.2)",     "$\\displaystyle l_3 = \\sum_{p,t} (\\log \\frac{1}{\\sqrt{2\\pi}} - \\frac{z_{3,p,t}^2}{2})$",

# Blank line to push 'Process Error prior density functions to 2nd page '
  "","",

  # Process error priors
  "(Pr.1)",      "$\\displaystyle p_{1} = \\sum_{t} (\\log \\frac{1}{\\sqrt{2\\pi}} - \\frac{\\omega_{t}^2}{2})$",
  "(Pr.2)",      "$\\displaystyle p_{2} = \\sum_{a} \\left( \\log \\frac{1}{\\sqrt{2\\pi}} - \\frac{\\left(\\omega^{init}_{a}\\right)^2}{2} \\right)$",
  "(Pr.3)",      "$\\displaystyle p_{3} = \\sum_{t} (\\frac{1}{\\sqrt{2\\pi}} - 0.5\\left(\\epsilon^{(M)}_{t}\\right)^2)$",

  # Leading parameter priors
  "(Pr.4)",      "$\\displaystyle p_{4} : M_{1951} \\sim \\log N(0.45,0.4)$",
  "(Pr.5)",      "$\\displaystyle p_{5} : h \\sim \\beta(20,9.84)$",
  "(Pr.6)",      "$\\displaystyle p_{6} : s^{50}_{p,g} \\sim \\log N(m^{s^{50}}_{g},s^{s^{50}}_{g})$",
  "(Pr.7)",      "$\\displaystyle p_{7} : s^{Step}_{p,g} \\sim \\log N(m^{s^{Step}}_{g},s^{s^{Step}}_{g})$",
  
  # Other priors
  "(Pr.8)",      "$\\displaystyle p_8 : q_s \\sim \\log N(0.5,0.5)$",
  "(Pr.9)",      "$\\displaystyle p_9 : \\tau^2_g \\sim IG(2,0.27)$",
  "(Pr.10)",     "$\\displaystyle p_{10} : \\log q^{pred}_{p,init} \\sim N(-4,-3)$",
  "(Pr.11)",     "$\\displaystyle p_{11} : \\epsilon^{(pred)}_{p,t} \\sim N(0,1)$",
  "(Pr.12)",     "$\\displaystyle p_{12} : \\psi_t \\sim \\log N(0.06,0.1)$",
  "(Pr.13)",     "$\\displaystyle p_{13} = \\sum_{g = 1}^3 \\rho_g^2$",
  "(Pr.14)",     "$\\displaystyle p_{14} = \\sum_{t} \\left( \\log \\frac{1}{\\sqrt{2\\pi}} - \\frac{\\left(\\log R_t - \\log \\hat{R}_t \\right)^2}{2\\sigma_R^2}\\right)$",
  "(Pr.15)",     "$\\displaystyle p_{15} : -\\log B_0$",
  "(Pr.16)",     "$\\displaystyle p_{16} = -\\log R_{bar}$",
  "(Pr.17)",     "$\\displaystyle p_{17} = -\\log R_{init}$",


  # Objective function
  "(F.1)",       "$f = l_1 + l_2 +l_3 + \\sum_{j = 1}^{17} p_j $",
)

colnames(statModelEqns) <- c("No.", "Equation")

kable( statModelEqns, escape = FALSE,
                      booktabs = TRUE,
                      format = kable_format,
                      longtable = TRUE,
                      caption = statModelEqnsCap,
                      align = c("l","l")) %>%
  kable_styling(latex_options = c("repeat_header"), font_size = 10) %>%
  kableExtra::group_rows("Observation model", 1, 2 ) %>%
  kableExtra::group_rows("Spawn index data likelihood", 3, 7 ) %>%
  kableExtra::group_rows("Age composition data likelihood", 8, 15 ) %>%
  kableExtra::group_rows("Predator consumption likelihood", 16, 18 ) %>%
  kableExtra::group_rows("Process error prior density functions", 19, 21 ) %>%
  kableExtra::group_rows("Priors on other parameters", 22, 35 ) %>%
  kableExtra::group_rows("Objective function (negative posterior density)", 36, 36 )





```

\renewcommand{\arraystretch}{1}

\clearpage

\blandscape

## Figures

```{r plotRPS, echo = FALSE, eval = FALSE, fig.cap =plotRPSCap, fig.width = 9, out.width = "6in"}
plotRPSCap <- "Scaled recruits per spawner calculated by number of spawner, by spawning biomass, and by eggs in PFMA 25, PFMA 24, and PFMA 23."

plotRpS_t(repList = fit3S)
```
\clearpage

```{r plotRPS2, echo = FALSE, eval = FALSE, fig.cap =plotRPS2Cap, fig.width = 9, out.width = "8in"}
plotRPS2Cap <- "percent difference in relative recruit per spawner in PFMA 25, PFMA 24, and PFMA 23."

plotDiffRpS_t(repList = fit3S)
```

\clearpage

```{r plotFAT, echo = FALSE, fig.cap = plotFATCap, out.width = "8in"}
plotFATCap <- "Foraging arena theory (FAT) relationships between predation rate (top row) and predator density (x-axis), and per-capita predation rate (bottom row) fit to SISCAH MLE estimates (purple points) for SSL, hbWinter, hbSpring, hbSummer, and hbFall. The relationships are fixed across stocks."
knitr::include_graphics(here::here(
  "Models/Sims/sim_1SpredMOM_minEMP_full",
  "simReport_files/figure-html",
  "FATFRpredRate-1.png"))
```

\clearpage

```{r plotPredConsump, echo = FALSE, fig.cap = plotPredConsumpCap, out.width = "8in"}
plotPredConsumpCap <- "Estimated predator consumption of herring (kt) by predator group over the historical period."
knitr::include_graphics(here::here(
  "Models/Sims/sim_1SpredMOM_minEMP_full",
  "simReport_files/figure-html",
  "predConsump-1.png"))
```

\clearpage

```{r plotPredMort, echo = FALSE, fig.cap = plotPredMortCap, out.width = "8in"}
plotPredMortCap <- "Estimated predation mortality rate by predator group over the historical period."
knitr::include_graphics(here::here(
  "Models/Sims/sim_1SpredMOM_minEMP_full",
  "simReport_files/figure-html",
  "predMort-1.png"))
```


\elandscape

\clearpage
```{=latex}
% Do not delete this
\end{appendices}
```